%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
  {(Typescript)} % Affiliation/role
  {\textcolor{darkblue}{\href{https://github.com/stumash/xradix}{xradix \ \faGithubSquare\acvHeaderIconSep} \href{https://stumash.github.io/xradix/}{\faMap}}} % Organization/group
  {Open Source Personal Project} % Location
  {} % Date(s)
  { % Description(s) of experience/contributions/knowledge
    \begin{cvitems}
    \item {A tested, performance-tested, and documented implementation of the \textcolor{darkblue}{\href{https://en.wikipedia.org/wiki/Radix_tree}{Radix Tree}} data structure. CI via Github Actions }
    \end{cvitems}
  }

%------------------------------------------------

\cventry
  {(VimL, Lua, Tree-Sitter)}
  {
    \textcolor{darkblue}{
      \href{https://github.com/tree-sitter/tree-sitter-scala/pulls?q=is\%3Apr+is\%3Aclosed+author\%3Astumash}{tree-sitter-scala \faGithubSquare}
      \href{https://github.com/stumash/shellvis}{shellvis \faGithubSquare}\ \ \
      \href{https://github.com/stumash/lcs.nvim}{lcs.nvim \faGithubSquare}\ \ \
      \href{https://github.com/stumash/snowball.nvim}{snowball.nvim \faGithubSquare}\ \ \
    }
  }
  {Open Source Personal Projects}
  {}
  {
    \begin{cvitems}
    \item {Contributions to a parser for the scala language for syntax highlighting}
    \item {A few \textcolor{darkblue}{\href{https://neovim.io/}{Neovim}} plugins}
    \end{cvitems}
  }

%------------------------------------------------

\cventry
  {(Java Tomcat, Nodejs, R, React, MongoDB)} % Affiliation/role
  {\textcolor{darkblue}{\href{http://conucourseplanner.online}{ConuCoursePlanner \color{darkblue}{\faLink}} \href{https://github.com/stumash/CoursePlanner}{\faGithubSquare\acvHeaderIconSep}}} % Organization/group
  {Personal Project} % Location
  {} % Date(s)
  { % Description(s) of experience/contributions/knowledge
    \begin{cvitems}
    \item {A tool to help freshmen select the course sequence of their curriculum. 100 unique active users per month}
    \item {Developed data pipeline: web scraper, data validator, and storage. Also wrote the core curriculum validation algorithm.}
    \end{cvitems}
  }

%------------------------------------------------

\cventry
  {(Java RMI, Concurrency/Parallelism, Two-Phase Commit)} % Affiliation/role
  {\textcolor{darkblue}{\href{https://github.com/stumash/DistributedSystemsProject}{Distributed Transactions Project \ \faGithubSquare\acvHeaderIconSep}}} % Organization/group
  {Distributed Systems, McGill} % Location
  {} % Date(s)
  { % Description(s) of experience/contributions/knowledge
    \begin{cvitems}
    \item {A toy distributed system for travel reservations (flights, cars, hotel rooms). Consensus via Two-Phase Commit. Wrote it all}
    \end{cvitems}
  }

%------------------------------------------------

\cventry
  {(Python, Cryptography, Multithreading)} % Affiliation/role
  {
    \textcolor{darkblue}{\href{https://github.com/CamiloGarciaLaRotta/Cebolla}{Cebolla (Onion Routing Network) \ \faGithubSquare\acvHeaderIconSep}}
    \href{https://www.youtube.com/watch?v=jR9N_xxLs6A}{\color{darkred}{\faYoutubePlay}}
  } % Organization/group
  {Telecomms \& Networks, McGill} % Location
  {} % Date(s)
  { % Description(s) of experience/contributions/knowledge
    \begin{cvitems}
    \item {Wrote all code for router node and directory node algorithms. Direct use of RSA and AES. Tested on 100-server cluster}
    \end{cvitems}
  }

%------------------------------------------------

\end{cventries}
