%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.1 (9/1/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry
 
\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-darknight} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION (CV HEADER)
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{Stuart}{Mashaal}
%\address{55 Sunnyside Avenue, Montreal, Quebec, Canada}
\mobile{(+1) 514 889 7509}
\email{stuart.mashaal@gmail.com}
\homepage{https://stumash.github.io}
\github{stumash}
\linkedin{stuart-mashaal}
\stackoverflow{4485898}{Captain\_Obvious}

\position{SOFTWARE ENGINEER | TN VISA CANDIDATE\ \color{darkblue}{\href{https://legalservicesincorporated.com/does-my-employer-have-to-sponsor-me-for-a-tn-visa-does-a-tn-visa-require-sponsorship/}{\faLink}}}
%\quote{``Make the change that you want to see in the world."} % A quote or statement

%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION (LETTER TITLE)
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

% FIXME
\newcommand{\companyname}{Warby Parker}
\newcommand{\jobtitle}{Software Engineer (Customer Experience)}

\recipient{Company Recruitment Team}{\companyname{}} % The company being applied to
\letterdate{\today} % The date on the letter, default is the date of compilation
\lettertitle{Job Application for \jobtitle{}} % The title of the letter
\letteropening{To Whom it May Concern,} % How the letter is opened
\letterclosing{Sincerely,} % How the letter is closed
\letterenclosure[Attached]{C.V.} % Any enclosures with the letter


% Specify the letter footer with 3 optional arguments: (<left>, <center>, <right>)
\makecvfooter{}{Stuart Mashaal~~~·~~~Cover Letter}{}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header

\makelettertitle % Print the title

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}

\lettersection{About Me}

I'm deeply passionate about clean and efficient code and have significant experience in many programming languages. I've written an implementation of Onion Routing in Python, a compiler for Go written in OCaml, and personal and school projects in Java and Javascript (fullstack web apps, mostly). I'm a Linux user at home, and love all things Bash.

I have a decent background in probability and statistics, and even used a Random Forest to improve the performance of a job scheduling system at my last internship at Nuance Communications.  

I also have a strong interest in scalability and distributed/cloud computing. I have taken extra courses in concurrency, distributed systems, and cloud computing. I have experience using AWS to deploy scalable web applications using Lambda, S3, EC2, and others. 

I've written various data scrapers over the years and have experience aggregating, cleaning, and storing data for later querying. I know how to get the job done using relational databases such as Postgre, and NoSQL databases such as MongoDB.

\lettersection{Why \jobtitle{} at \companyname{}}

Well, for one thing, I love the idea of Warby Parker as a business. Luxottica was keeping glasses expensive, and Warby Parker used vertical integration and branding to challenge the status quo, bring prices down, and steal market share.

But, for another, I expect the company culture at WP to be a good fit for me. My most rewarding work experience so far was at an online advertising company called SourceKnowledge. What made my time there so meaningful was the culture of open communication. If I had to speak to anyone in the company to get my work done, there was no red tape in the way. I found this incredibly helpful, and expect a similar situation at WP.

But on a technical level, I'm excited to work with other engineers that have a passion for clean, readable, and fast code. I'm eager to raise the quality of my work by meeting the high standards of software quality at WP.

\lettersection{In\ Closing}

Thanks for your time and consideration. I hope to hear from you soon.

%Given my experience, skills, and interests, I think I'm a good fit for the position and can join the technology team at \companyname{} in continuing to deliver excellent customer experience tools.

%Thank you for your time and consideration.

\end{cvletter}

%----------------------------------------------------------------------------------------

\makeletterclosing % Print the signature and enclosures

\end{document}
